---
title: "Skills4EOSC WP 6.1: Mapping Professional Networks Search"
author: "Laurence Horton"
date: "2022-12-16"
---

# Skills4EOSC WP 6.1: Mapping Professional Networks Search

This is intended to help with the searching for Open Science related professional networks by automating the search teams in a browser based on search string criteria and a country internet domain.

By default it is set to English language searches, using the DuckDuckGo search engine. Both can be changed with according to the user's wishes.

This is not a web scraping tool. It is just for searching. The results will still need browsing, appraisal, and selection.

It works for those with authorisation to access the Google sheet "Professional networks"

Search strings were created by:
* Mareike Buss (CBS/DeiC)
* Emily Thorsson Schöller (CBS/DeiC)

```{r library}
library(RCurl)
library(googlesheets4)
library(tidyverse)
```

```{r read google sheet into R}
# Will need to authenticate to allow Tidyverse to access your google account.
# Need to manually select the "See, edit, create and delete all your Google Sheets spreadsheets. Learn more" option when authenticating.
searches <-
  read_sheet(
    "https://docs.google.com/spreadsheets/d/1VxjTdvWuc-E7dCDEaYosPeeL22wAvevPL5K3yO43L6g/edit#gid=0",
    sheet = "Search strings and searches",
    skip = 2
  )
```

```{r subset search strings}
# If you need to search a different language, point to that specific column, i.e. "Search strings Denmark"
search_strings <- searches %>%
  select("Search strings Ireland") %>%
  rename("Search strings" = 1)
```

```{r convert search strings to url text}
# This converts the search strings into a string that can be added to the google search url.
search_strings$`Search strings` <-
  gsub(" \\[country\\]", " ", search_strings$`Search strings`)
search_strings$`Search strings` <-
  gsub(",", "+OR", search_strings$`Search strings`)
search_strings$`Search strings` <-
  trimws(
    search_strings$`Search strings`,
    which = c("both", "left", "right"),
    whitespace = "[ \t\r\n]"
  )
search_strings$`Search strings` <-
  gsub(" ", "+", search_strings$`Search strings`)
```

```{r split the search terms into character types}
Artificial_intelligence <- as.character(search_strings[1, ])
Data_analytics <- as.character(search_strings[2, ])
Data_curators <- as.character(search_strings[3, ])
Data_sharing <- as.character(search_strings[4, ])
Data_stewardship <- as.character(search_strings[5, ])
Data_storage <- as.character(search_strings[6, ])
FAIR_OR_FAIR_data <- as.character(search_strings[7, ])
High_performance_computing <- as.character(search_strings[8, ])
High_performance_data_analytics <- as.character(search_strings[9, ])
Open_access <- as.character(search_strings[10, ])
Open_code_and_software <- as.character(search_strings[11, ])
Open_science <- as.character(search_strings[12, ])
Replicability <- as.character(search_strings[13, ])
Reproducibility <- as.character(search_strings[14, ])
Research_data_management <- as.character(search_strings[15, ])
Research_infrastructure <- as.character(search_strings[16, ])
Scientific_integrity <- as.character(search_strings[17, ])
Transparency <- as.character(search_strings[18, ])
```

```{r search URL prefix}
search <- "https://duckduckgo.com/?q="
```

```{r}
# ISO 3166-1 alpha-3 country code and ccTLDs country code top-level domains
AUT <- ":.AT"
BEL <- ":.BE"
CHE <- ":.CH"
CZE <- ":.CZ"
DEU <- ":.DE"
DNK <- ":.DK"
ESP <- ":.ES"
EST <- ":.EE"
FIN <- ":.FI"
FRA <- ":.FR"
GBR <- ":.UK"
GRC <- ":.GR"
HUN <- ":.HU"
IRE <- ":.IE"
ISL <- ":.IS"
ITA <- ":.IT"
LTU <- ":.LT"
NLD <- ":.NL"
NOR <- ":.NO"
POL <- ":.PL"
PRT <- ":.PT"
SVK <- ":.SK"
SWE <- ":.SE"
```

```{r}
# Remember to match country to column country selected
country <- IRE
```

```{r function for search}
geturlname <- function(name) {
  h <- getCurlHandle()
  z <- getURL(paste0(search, name, country),
              followlocation = TRUE,
              curl = h)
  getCurlInfo(h)$effective.url # Stops a redirect to first link on the search
}
```

## Search terms
```{r artificial intelligence}
browseURL(geturlname(Artificial_intelligence))
```
```{r data analytics}
browseURL(geturlname(Data_analytics))
```
```{r data curators}
browseURL(geturlname(Data_curators))
```
```{r data sharing}
browseURL(geturlname(Data_sharing))
```
```{r data stewardship}
browseURL(geturlname(Data_stewardship))
```
```{r data storage}
browseURL(geturlname(Data_storage))
```
```{r fair or fair data}
browseURL(geturlname(FAIR_OR_FAIR_data))
```
```{r high performance computing}
browseURL(geturlname(High_performance_computing))
```
```{r hpda}
browseURL(geturlname(HPDA))
```
```{r open access}
browseURL(geturlname(Open_access))
```
```{r open code and software}
browseURL(geturlname(Open_code_and_software))
```
```{r open science}
browseURL(geturlname(Open_science))
```
```{r replicability}
browseURL(geturlname(Replicability))
```
```{r reporoducability}
browseURL(geturlname(Reproducibility))
```
```{r research data management}
browseURL(geturlname(Research_data_management))
```
```{r research infastructure}
browseURL(geturlname(Research_infrastructure))
```
```{r scientific integrity}
browseURL(geturlname(Scientific_integrity))
```
```{r transparency}
browseURL(geturlname(Transparency))
```